We assume that the continuous-time hybrid dynamical system under test
can be numerically simulated using a given $\simulate$ function. SUch
a function is a state based deterministic numerical simulator of the
form $\x'=\simulate(t,\x)$, where a new state $\x'$ reachable after
time $t$ from $\x$ can be computed numerically whithin `acceptable'
precision. Given a time bounded LTL property $\phi$, we now present a
best effort search to find a counter-example $\pi$ to $\phi$ which can
be reproduced using the given $\simulate$.

What and Why?
\begin{itemize}
    \item Verification/falsification approaches use model
        based on symbolic dynamics. SECAM finds falsifications using
        only simulations. Can we find an approach which is of
        intermediate complexity by recovering some model of the system
        from observed simulations? We can use local PWA modeling.
\end{itemize}

How?
\begin{itemize}
    \item Generate data: relations
    \item Build local PWA models of the system by discretizing space
          and time.
    \item Use an SMT solver to check time bounded
          properties (Bounded model checking).
    \item Refine
\end{itemize}

What deficiencies are we addressing here of the current
appraoches (SECAM, S-Taliro, others)?

\subsection{Building a Model} We would like to build a model of the
system that is amenable to falsification (or verification in the case
of white-box systems). A naive solution would be to describe all the
behaviors of the system using a PWA model, where each region on the
state space is associated with a set of affine dynamics. Such a
discretization of the continuous hybrid dynamical system is amenable
to model checking and has been explored in the past in several
works~\cite{}. The problem lies in the scalability. Depending upon the
dynamics of the system, an intractable number of paritions might be
necessary to get accurate enough PWA model. Moreover, identifying such
paritions automatically is a hard problem~\cite{} (check nimit's paper
for citations).

\subsection{Finding a counterexample} Once we have the pwa model we
use an SMT solver to check the property $\phi$ for bounded time.

\subsection{Refinement} Once a counterexample for $\phi$ against the
pwa model is found, it needs to be checked if the numerical simulator
satisfies it. This is due to the discrepencies between the approximate
PWA model and numerical simulator. A confirmed violation at this stage
successfully terminates the search for the violation. Otherwise, a
refinement of the PWA model is necessary.
Refinement ideas?
